\Huge \textcolor{titleTextColor}{ \textsf{\textbf{ \fontsize{85}{60}\selectfont How innovations thrive in GRASS GIS }} }

### 2017-02-21 grassposter/2017_NCGIS_How_innovations_thrive/poster.tex
authors cosmentics
git-svn-id: https://svn.osgeo.org/grass/grass-promo@70652 15284696-431f-4ddb-bdfa-cd5b030d7da7

\author{
V\'{a}clav Petr\'{a}\v{s}\inst{1},
Yann Chemin,
Martin Landa\inst{2},
Thomas Leppelt\inst{3},
Pietro Zambelli\inst{4},
Luca Delucchi\inst{5},
Margherita Di Leo\inst{6}
S\"{o}ren Gebbert,
Markus Neteler\inst{7},
}
\institute{
\instlist{1}NCSU, USA;
\instlist{2}FCE CTU in Prague, Czech Republic;
\instlist{3}Deutscher Wetterdienst, Germany;
\instlist{4}EURAC, Italy;
\instlist{5}CRI, FEM, Italy;
\instlist{6}EC-JRC, Italy
\instlist{7}mundialis GmbH \& Co. KG, Germany;
}

>>>>

\author{
V\'{a}clav Petr\'{a}\v{s}\inst{1},
Yann Chemin,
Martin Landa\inst{2},
Thomas Leppelt\inst{3},
Pietro Zambelli\inst{4},
Luca Delucchi\inst{5},
Margherita Di Leo\inst{6},
S\"{o}ren Gebbert,
Markus Neteler\inst{7}
}
\institute{
\instlist{1}NCSU, USA;
\instlist{2}FCE CTU in Prague, Czech Republic;
\instlist{3}Deutscher Wetterdienst, Germany;
\instlist{4}EURAC, Italy;
\instlist{5}CRI, FEM, Italy;
\instlist{6}EC-JRC, Italy;
\instlist{7}mundialis GmbH \& Co. KG, Germany
}
